---
title: "Dave's Analysis 2 for Data Mining HW 1"
output:
  html_document:
    df_print: paged
---
Reading in the restaurant data with the arules package.
```{r}
library(arules)
library(tidyverse)
menu <- read_csv("../restaurantData.csv")
```

## Background
A restaurant owner has a core menu that has remained constant throughout the past two years, while many other dishes have rotated on and off the menu. The owner has prepared a dataset of all orders containing elements of that core menu in which the customer also ordered wine. The dataset has 3 columns: orderNumber which identifies each individual person’s order at a table, order which itemizes the order’s components, and type which provides the type of item in the order (takes one of 3 values: ‘Meat’, ‘Side’, ‘Wine’).

## Task
The restaurant owner would like to add wine suggestions to the menu next to each meat and analyze her customer ordering habits in general. She is also interested in showing a picture of a popular meal of hers in an ad in Gourmet Diner magazine. Your job is to address her interests and also to report anything else of interest in terms of customer ordering habits, all in a nice summary report that is complete but to the point.


#### Overview of the dataset
```{r}
str(menu)
head(menu)
```
#### Converting dataframe to transactions object and dropping type variable
```{r}
menu_2 <- menu %>% 
  select(order,orderNumber) %>% 
  modify_at("orderNumber", as.numeric) %>% 
  modify_at("order", as_factor) %>% 
  as.data.frame

  
trans <- as(split(menu_2[,"order"], menu_2[,"orderNumber"]), "transactions")
```

#### Looking at the first 25 observations
```{r}
inspect(trans[1:5])
```

#### Frequency of items
```{r}
itemFrequency(trans)
```

#### Visualizing the frequencies
```{r}
itemFrequencyPlot(trans, support = 0.1)
itemFrequencyPlot(trans, topN = 20 )
```


#### Visualizing the sparse matrix of the first 100 observations
```{r}
image(trans[1:50])
```


#### Learning the association rules from the dataset with default settings
```{r}
apriori(trans)
```

#### Setting the confidence levels and support to learn more rules
```{r}
rules <- apriori(trans, parameter = list(support = 0.01, confidence = 0.25, minlen = 2))
```

#### Checking out the rules
```{r}
summary(rules)
```


#### 112 rules were discovered with parameter tweaks
```{r}
inspect(rules[1:10])
```
#### Looks like they were sorted by ascending support.
#### Inspecting with sort by lift.
```{r}
inspect(sort(rules, by = "lift")[1:10])
```

#### Find unique wines
```{r}
wine <- menu %>% 
  filter(type == "Wine") %>% 
  distinct(order) %>% 
  pull()
wine
```

#### Find subset of rules for 4 wine types
```{r}
merlot <- subset(rules, items %in% wine[1])
inspect(sort(merlot, by = "confidence")[1:10])
```

6.25 times more likely to see a Blackstone Merlot with Filet Mignon than we are to see one at random.
68.3% condidence that customers will order Blackstone Merlot with Filet Mignon

```{r}
pinot_bianco <- subset(rules, items %in% wine[2])
inspect(sort(pinot_bianco, by = "confidence")[1:20])
```

1.67 times more likely to see a Cantina Pinot Bianco with Pork Tenderloin than we are to see one at random.
94.3% condidence that customers will order Cantina Pinot Bianco with Pork Tenderloin.

```{r}
pinot_noir <- subset(rules, items %in% wine[3])
inspect(sort(pinot_noir, by = "confidence"))
```

No values for Meiomi Pinot Noir in the consequent(RHS).
37.3% condidence that customers will order Meiomi Pinot Noir with Roast Chicken.


```{r}
chardonnay <- subset(rules, items %in% wine[4])
inspect(sort(chardonnay, by = "confidence"))
```

2.75 times more likely to see a Duckhorn Chardonnay with Roast Chicken than we are to see one at random.
48.4% condidence that customers will order Duckhorn Chardonnay with Roast Chicken.

```{r}
duck <- subset(rules, items %in% c("Duck"))
inspect(sort(duck, by = "lift"))
```

2.46 times more likely to see a Duckhorn Chardonnay with Duck than we are to see one at random.

#### Find the top order meal list by support (items most frequently order together)
```{r}
meal_rules <- apriori(trans, parameter = list(support = 0.05, confidence = 0.01, minlen = 3))
```

```{r}
summary(meal_rules) 
```

```{r}
inspect(sort(meal_rules, by = "support"))
```

#### Finding the items with greatest confidence
```{r}
gen_rules <- apriori(trans, parameter = list(support = 0.05, confidence = 0.25, minlen = 2))
summary(gen_rules)
```

#### sorting meals by highest confidence
```{r}
inspect(sort(gen_rules, by = c("support", "confidence")))
```

