---
title: "Dave's Homework 1 Analysis"
output:
  html_document:
    df_print: paged
---

Reading in the restaurant data with the arules package.
```{r}
library(arules)
menu <- read.transactions("../restaurantData.csv", sep = ",")
```

## Background
A restaurant owner has a core menu that has remained constant throughout the past two years, while many other dishes have rotated on and off the menu. The owner has prepared a dataset of all orders containing elements of that core menu in which the customer also ordered wine. The dataset has 3 columns: orderNumber which identifies each individual person’s order at a table, order which itemizes the order’s components, and type which provides the type of item in the order (takes one of 3 values: ‘Meat’, ‘Side’, ‘Wine’).

## Task
The restaurant owner would like to add wine suggestions to the menu next to each meat and analyze her customer ordering habits in general. She is also interested in showing a picture of a popular meal of hers in an ad in Gourmet Diner magazine. Your job is to address her interests and also to report anything else of interest in terms of customer ordering habits, all in a nice summary report that is complete but to the point.


#### Overview of the dataset
```{r}
str(menu)
summary(menu)
```

#### Looking at the first 25 observations
```{r}
inspect(menu[1:25])
```

#### Frequency of items
```{r}
itemFrequency(menu[,1:3])
```

#### Visualizing the frequencies
```{r}
itemFrequencyPlot(menu, support = 0.1)
itemFrequencyPlot(menu, topN = 20 )
```


#### Visualizing the sparse matrix of the first 100 observations
```{r}
image(menu[1:3])
```


#### Learning the association rules from the dataset with default settings
```{r}
apriori(menu)
```

#### Setting the confidence levels and support to learn more rules
```{r}
rules <- apriori(menu, parameter = list(support = 0.006, confidence = 0.25, minlen = 2))
```

#### Checking out the rules
```{r}
summary(rules)
```


#### 18 rules were discovered with parameter tweaks
```{r}
inspect(rules)
```
#### Looks like they were sorted by ascending support.
#### Inspecting with sort by lift.
```{r}
inspect(sort(rules, by = "lift"))
```

#### Find subset of rules for main courses
```{r}
mains_rules <- subset(rules, items %in% c("Filet Mignon", "Roast Chicken", "Duck", "Pork Tenderloin"))
inspect(mains_rules)
```


